---
title: "Aides Drug"
author: "Put your name here!"
date: "put the date here"
output:
  pdf_document: default
  html_document: default
params:
  TheData:
    choices:
    - avast
    - avastF
    - avastM
    - avastD
    - avastQ
    input: select
    label: TheData
    value: avastF
---




```{r setup, include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avastF <- filter(avast,sex=="gal")
avastM <- filter(avast,sex=="guy")
avastD <- filter(avast,DrugUser=="yes")
avastQ <- filter(avast,LGBTQ=="gay")


```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. Finish this!




<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r include=FALSE}
if (params$TheData=="avast")  {trialtbl <-xtabs(~infected+treatment,data=avast) 
plottitle <- "everybody"}
if (params$TheData=="avastF")  {trialtbl<-xtabs(~infected+treatment,data=avastF) 
plottitle <- "Just Gals"}
if (params$TheData=="avastM")  {trialtbl<-xtabs(~infected+treatment,data=avastM) 
plottitle <- "Just Guys"}
if (params$TheData=="avastD")  {trialtbl<-xtabs(~infected+treatment,data=avastD) 
plottitle <- "Only the Drug Users"}
if (params$TheData=="avastQ")  {trialtbl<-xtabs(~infected+treatment,data=avastQ) 
plottitle <- "Only Light in the Sandals"}

```

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->


# Results for `r plottitle`

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(trialtbl,type = "percent",main=plottitle)
```

### Numerical Results

<!--Display numerical evidence as to the effectiveness of the vaccine with explanations !--> 

```{r}
colPerc(trialtbl)
rowPerc(trialtbl)
```




## Inferential results

<!--Display inferential evidence as to the effectiveness of the vaccine with explanations and interpretations!-->

```{r}
chisqtestGC(trialtbl, graph = TRUE)
```
```{r}
fisher.test(trialtbl)
```



# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
